The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-12 manuscript/manuscript.Rnw
update authors list and affils

\begin{document}
\author[1,2]{Michael R. McGowen}
\author[1]{Don Armstrong}
\author[1]{Amy Weckle}
\author[1]{Jason Caravas}
\author[3]{Dalen Agnew}
\author[4]{Kurt Benirschke}
\author[5]{Sue Savage-Rumbaugh}
\author[6,7]{Chong Jai Kim}
\author[8]{Günter P. Wagner}
\author[6]{Roberto Romero}
\author[1,6,9,*]{Derek E. Wildman}
\title{The evolution of gene expression in the term placenta of viviparous mammals}
% These are all wrong, but we'll change them later.
\affil[1]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\affil[2]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\affil[3]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\affil[4]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\affil[5]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\affil[6]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\affil[7]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\affil[8]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\affil[9]{Department of Obstetrics and Gynecology, Wayne State University School of Medicine, Detroit, MI, USA}
\affil[*]{To whom correspondence should be addressed}
\date{\today}

>>>>

\begin{document}
\author[1]{Don Armstrong}
\author[2]{Michael R. McGowen}
\author[1]{Amy Weckle}
\author[3]{Jason Caravas}
\author[4]{Dalen Agnew}
\author[5]{Kurt Benirschke}
\author[6]{Sue Savage-Rumbaugh}
\author[7,8]{Chong Jai Kim}
\author[9]{Günter P. Wagner}
\author[7]{Roberto Romero}
\author[1,6,10,*]{Derek E. Wildman}
\title{The evolution of gene expression in the term placenta of viviparous mammals}
% These are all wrong, but we'll change them later.
\affil[1]{Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\affil[2]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\affil[3]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\affil[4]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\affil[5]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\affil[6]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\affil[7]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\affil[8]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\affil[9]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\affil[10]{Department of Molecular and Integrative Physiology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\affil[*]{To whom correspondence should be addressed}
\date{\today}
